AA Distributed Software Development Methodology

### 2013-06-02 front-matter.tex
merged hybrid commit a45db4aa47012
tentando author bulk package
lista de autores ficou baoa

\author{%
Renato~Fabbri \and Ricardo~Fabbri \and Vilson Vieira \and Alexandre Negr\~{a}o \and Lucas Zambianchi
\and Marcos Mendon\c{c}a \and Danilo Shiga\\[1em]
\small{
Instituto de F\'{i}sica de S\~{a}o Carlos (IFSC), Universidade de
S\~{a}o Paulo (USP), Brazil}\\[0.5em]
\small{Instituto Polit\'{e}cnico, Universidade do Estado do Rio de
Janeiro, Nova Friburgo, RJ, Brazil}\\[0.5em]
\url{LabMacambira.sourceforge.net}.
}

>>>>

%\author{%
%Renato~Fabbri \and Ricardo~Fabbri \and Vilson~Vieira \and Alexandre~Negr\~{a}o \and Lucas~Zambianchi
%\and Marcos~Mendon\c{c}a \and Daniel~Penalva \and Danilo~Shiga\\[1em]
%\small{
%Instituto de F\'{i}sica de S\~{a}o Carlos (IFSC), Universidade de
%S\~{a}o Paulo (USP), Brazil}\\[0.5em]
%\small{Instituto Polit\'{e}cnico, Universidade do Estado do Rio de
%Janeiro, Nova Friburgo, RJ, Brazil}\\[0.5em]
%\url{LabMacambira.sourceforge.net}.
%}

\author[1,3]{Renato Fabbri\thanks{renato.fabbri@gmail.com}}
\author[2,3]{Ricardo Fabbri\thanks{rfabbri@iprj.uerj.br}}
\author[1,3]{Vilson Vieira\thanks{vilson@void.cc}}
\author[3]{Alexandre Negr\~{a}o}
\author[3]{Lucas Zambianchi}
\author[3]{Marcos~Mendon\c{c}a}
\author[1,3]{Daniel Penalva}
\author[3]{Danilo Shiga}
\affil[1]{\small Physics Insitute at S\~{a}o Carlos (IFSC), University of S\~{a}o Paulo (USP), Brazil}
\affil[2]{\small Polytechnic Institute (IPRJ), State University of Rio de Janeiro (UERJ), Nova Friburgo, Brazil}
\affil[3]{\small \url{LabMacambira.sourceforge.net}}

\renewcommand\Authands{ and }
